\emph{Ab initio} Calculations of Intramolecular Exciton Transfer with Reduced Modes in Donor-Bridge-Acceptor Species

### 2016-04-27 Chapters/chap1/introduction.tex
Revision
Revision according to college readers

%!TEX root = /Users/tcya/Dropbox/PhDthesis/thesis.tex
\chapter{Introduction}\footnotetext{Part of this chapter has been published in Xunmo Yang and E. R. Bittner, The Journal of Physical Chemistry A\textbf{118}, 5196 (2014)}
\section{Introduction}

@@

A number of years ago,  our group developed a time-convolutionless  master equation approach for computing
state-to-state rates in which the coupling between  states depends upon the
nuclear coordinates\cite{pereverzev2006time}. This approach incorporates a fully quantum
mechanical treatment of both the nuclear and electronic degrees of freedom and recovers the
well-known Marcus expression in the semiclassical limit.  The model is parameterized by the
vibrational normal mode frequencies, and the electronic energies and energy derivatives
at a reference configuration.  The approach has been used by our group to compute state-to-state
transition rates in semi-empirical models for organic semiconducting light-emitting diode and photovoltaics
\cite{tamura2008phonon,tamura2007exciton,bittner2014noise,singh2009fluorescence}.
Our work here represents the first time this approach has been used within the context of a fully {\em ab initio} quantum
chemical model.   As such, this present work provides an important benchmark of the approach since all parameters will be determined
using state-of-the-art quantum chemical methods
and results compared to both theoretical and experimental
rates.

@@

\begin{figure}[!t]
\includegraphics[width=0.95\columnwidth]{Chapters/chap2/adia_vs_diabatic.png}
\caption{Sketch of adiabatic and diabatic representations for two-state system. Compared to adiabatic representation, diabatic representation has smoother energy surfaces and couplings.
}
\label{adiaDiab}
\end{figure}

>>>>

%!TEX root = /Users/tcya/Dropbox/XunmoYang/PhDthesis/thesis.tex
\chapter{Introduction}\footnotetext{Part of this chapter has been published in Xunmo Yang and E. R. Bittner, Intramolecular Charge- and Energy-Transfer Rates with Reduced Modes: Comparison to Marcus Theory for Donor–Bridge–Acceptor Systems. The Journal of Physical Chemistry A\textbf{118}, 5196 (2014)}
\section{Introduction}

@@

A number of years ago,  our group developed a time-convolutionless  master equation approach for computing
state-to-state rates in which the coupling between  states depends upon the
nuclear coordinates\cite{pereverzev2006time}. This approach incorporates a fully quantum-mechanical treatment of both the nuclear and electronic degrees of freedom and recovers the
well-known Marcus expression in the semiclassical limit.  The model is parameterized by the
vibrational normal mode frequencies, and the electronic energies and energy derivatives
at a reference configuration.  The approach has been used by our group to compute state-to-state
transition rates in semi-empirical models for organic semiconducting light-emitting diode and photovoltaics
\cite{tamura2008phonon,tamura2007exciton,bittner2014noise,singh2009fluorescence}.
Our work here represents the first time this approach has been used within the context of a fully {\em ab initio} quantum-chemical model.   As such, this present work provides an important benchmark of the approach since all parameters will be determined
using state-of-the-art quantum-chemical methods
and results compared to both theoretical and experimental
rates.

@@

\begin{figure}[!t]
\includegraphics[width=0.95\columnwidth]{Chapters/chap2/adia_vs_diabatic.pdf}
\caption{Sketch of adiabatic and diabatic representations for two-state system. Compared to adiabatic representations, diabatic representation has smoother energy surfaces and couplings.
}
\label{adiaDiab}
\end{figure}

### 2016-04-27 Chapters/chap4/chap4.tex
Revision according to college readers

\begin{figure*}[!h]
\includegraphics[width=0.71\columnwidth]{Chapters/chap4/Images/scheme.jpg}
\caption{The sketch of ET pathways. For PTZ-CH\textsubscript{2}-Pt-NAP, the CT $\rightarrow$ CSS step can be fully suppressed by intermediate infrared excitation. Reprinted with permission from Ref.~\cite{delor2015mechanism}.\label{ETscheme}}
\end{figure*}

@@

\begin{figure}[]
\subfloat[]{\includegraphics[width=0.84\columnwidth]{Chapters/chap4/Images/plmT12.png}}\\
\subfloat[]{\includegraphics[width=0.84\columnwidth]{Chapters/chap4/Images/plmT13.png}}
% \subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT31.png}}\\
% \subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT32.png}}
\caption{
Projection of primary mode of (a) CSS $\rightarrow$ \textsuperscript{3}NAP, (b) CT $\rightarrow$ \textsuperscript{3}NAP calculated at \textsuperscript{3}NAP geometry onto the normal modes of \textsuperscript{3}NAP. Embedded molecule shows the atomic displacement vectors of primary mode. If we focus on the C$\equiv$C bonds, PLMs are like
PTZ-Ph-C$\equiv$C-Pt-C$\protect\overset{\longleftrightarrow}{\equiv}$C-NAP
in (a) and
PTZ-Ph-$\protect\overset{\longleftarrow}{C}\equiv\protect\overset{\longrightarrow}{C}$-Pt-$\protect\overset{\longrightarrow}{C}\equiv\protect\overset{\longleftarrow}{C}$-NAP
in (b).}\label{projT1}
\end{figure}

\begin{figure}[]
% \subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT12.png}}\\
% \subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT13.png}}
\subfloat[]{\includegraphics[width=0.85\columnwidth]{Chapters/chap4/Images/plmT31.png}}\\
\subfloat[]{\includegraphics[width=0.85\columnwidth]{Chapters/chap4/Images/plmT32.png}}
\caption{
Projection of primary mode of (a) CT $\rightarrow$ \textsuperscript{3}NAP, and (b) CT $\rightarrow$ CSS calculated at CT geometry onto the normal modes of CT. Embedded molecule shows the atomic displacement vectors of primary mode. If we focus on the C$\equiv$C bonds, PLMs are like
PTZ-Ph-$\protect\overset{\longleftarrow}{C}\equiv\protect\overset{\longrightarrow}{C}$-Pt-$\protect\overset{\rightarrow}{C}\equiv\protect\overset{\leftarrow}{C}$-NAP
in (a) and
PTZ-Ph-$\protect\overset{\longleftarrow}{C}\equiv\protect\overset{\longrightarrow}{C}$-Pt-$\protect\overset{\leftarrow}{C}\equiv\protect\overset{\rightarrow}{C}$-NAP
in (b).
}\label{projT3}
\end{figure}

>>>>

\begin{figure*}[!h]
\includegraphics[width=0.71\columnwidth]{Chapters/chap4/Images/scheme.jpg}
\caption{The sketch of ET pathways. For PTZ-CH\textsubscript{2}-Pt-NAP, the CT $\rightarrow$ CSS step can be fully suppressed by intermediate infrared excitation. Adapted with permission from Ref.~\cite{delor2015mechanism}.\label{ETscheme}}
\end{figure*}

@@

\begin{figure}[]
\subfloat[]{\includegraphics[width=0.84\columnwidth]{Chapters/chap4/Images/plmT12.pdf}}\\
\subfloat[]{\includegraphics[width=0.84\columnwidth]{Chapters/chap4/Images/plmT13.pdf}}
% \subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT31.pdf}}\\
% \subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT32.pdf}}
\caption{
Projection of primary mode of (a) CSS $\rightarrow$ \textsuperscript{3}NAP, (b) CT $\rightarrow$ \textsuperscript{3}NAP calculated at \textsuperscript{3}NAP geometry onto the normal modes of \textsuperscript{3}NAP. Embedded molecule shows the atomic displacement vectors of primary mode. If we focus on the C$\equiv$C bonds, PLMs are like
PTZ-Ph-C$\equiv$C-Pt-C$\protect\overset{\longleftrightarrow}{\equiv}$C-NAP
in (a) and
PTZ-Ph-$\protect\overset{\longleftarrow}{C}\equiv\protect\overset{\longrightarrow}{C}$-Pt-$\protect\overset{\longrightarrow}{C}\equiv\protect\overset{\longleftarrow}{C}$-NAP
in (b).}\label{projT1}
\end{figure}

\begin{figure}[]
% \subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT12.pdf}}\\
% \subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT13.pdf}}
\subfloat[]{\includegraphics[width=0.85\columnwidth]{Chapters/chap4/Images/plmT31.pdf}}\\
\subfloat[]{\includegraphics[width=0.85\columnwidth]{Chapters/chap4/Images/plmT32.pdf}}
\caption{
Projection of primary mode of (a) CT $\rightarrow$ \textsuperscript{3}NAP, and (b) CT $\rightarrow$ CSS calculated at CT geometry onto the normal modes of CT. Embedded molecule shows the atomic displacement vectors of primary mode. If we focus on the C$\equiv$C bonds, PLMs are like
PTZ-Ph-$\protect\overset{\longleftarrow}{C}\equiv\protect\overset{\longrightarrow}{C}$-Pt-$\protect\overset{\rightarrow}{C}\equiv\protect\overset{\leftarrow}{C}$-NAP
in (a) and
PTZ-Ph-$\protect\overset{\longleftarrow}{C}\equiv\protect\overset{\longrightarrow}{C}$-Pt-$\protect\overset{\leftarrow}{C}\equiv\protect\overset{\rightarrow}{C}$-NAP
in (b).
}\label{projT3}
\end{figure}

### 2016-04-27 FrontBackmatter/Abstract.tex
Revision according to college readers

%*******************************************************
% Abstract ( 350 words max ! )
%*******************************************************
\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Abstract}
% Essential microscopic aspects of activated transport in liquids, which
% precedes the glass transition, have evaded explanation for
% decades. These poorly understood aspects include: the molecular
% underpinning of the excess, configurational entropy; the transition
% state configurations for the activated transport; the chemical origin
% of the fragile vs. strong liquid behavior; and many others. This
% dissertation puts forth a radically novel way to address these open
% questions, in which liquids near their glass transition are viewed as
% structurally degenerate assemblies of strongly interacting, local
% sources of frozen-in stress. The thermodynamics and activated barriers
% for rearrangement of this stress field have been mapped onto a
% Heisenberg model with six-dimensional spins. A meanfield analysis of
% the spin model has shown glasses can be viewed as frozen-in patterns
% of shear stress and/or uniform compression/dilation, the two extremes
% corresponding to the strong and fragile behaviors. A self-consistent
% elasticity theory of aperiodic, metastable solids emerges in the
% present analysis; it supersedes the traditional elasticity theory,
% which fails to self-consistently account for the structural degeneracy
% stemming from the inherent mismatch between cohesive forces and steric
% repulsion.  The observable elastic constants self-consistently emerge
% in the present theory similarly to how the dielectric susceptibility
% is determined by the properties of molecular dipoles. First
% simulations of the spin model have been carried out. In addition to
% direct observations of transition states for the activated transport,
% several key features of the glass transition are yielded by the spin
% model, including a strongly non-exponential, non-Arrhenius character
% of the relaxations and its correlation with the Poisson ratio of the
% substance.
We present a new, fully {\em ab initio} approach for computing intramolecular charge and
energy transfer rates.  Using a time-convolutionless master equation approach, parameterized
with couplings obtained from an accurate quantum chemical approach, we  benchmark the approach
against  experimental results and predictions from Marcus theory for triplet energy transfer for a
series of donor-bridge-acceptor systems.
An important component of our analysis is the use of a projection operator scheme
that parses out specific internal nuclear motions that accompany
the electronic transition.
Using an iterative Lanczos method, we  concentrate the coupling between the electronic and nuclear
degrees of freedom into a small number of reduced harmonic modes.
We find that  using only a single reduced mode--termed the ``primary mode'' or ``Lanczos modes'',
 one obtains an accurate evaluation of the golden-rule rate constant and
insight into the nuclear motions responsible for coupling the initial and final electronic states.

>>>>

%*******************************************************
% Abstract ( 350 words max ! )
%*******************************************************
\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Abstract}
% Essential microscopic aspects of activated transport in liquids, which
% precedes the glass transition, have evaded explanation for
% decades. These poorly understood aspects include: the molecular
% underpinning of the excess, configurational entropy; the transition
% state configurations for the activated transport; the chemical origin
% of the fragile vs. strong liquid behavior; and many others. This
% dissertation puts forth a radically novel way to address these open
% questions, in which liquids near their glass transition are viewed as
% structurally degenerate assemblies of strongly interacting, local
% sources of frozen-in stress. The thermodynamics and activated barriers
% for rearrangement of this stress field have been mapped onto a
% Heisenberg model with six-dimensional spins. A meanfield analysis of
% the spin model has shown glasses can be viewed as frozen-in patterns
% of shear stress and/or uniform compression/dilation, the two extremes
% corresponding to the strong and fragile behaviors. A self-consistent
% elasticity theory of aperiodic, metastable solids emerges in the
% present analysis; it supersedes the traditional elasticity theory,
% which fails to self-consistently account for the structural degeneracy
% stemming from the inherent mismatch between cohesive forces and steric
% repulsion.  The observable elastic constants self-consistently emerge
% in the present theory similarly to how the dielectric susceptibility
% is determined by the properties of molecular dipoles. First
% simulations of the spin model have been carried out. In addition to
% direct observations of transition states for the activated transport,
% several key features of the glass transition are yielded by the spin
% model, including a strongly non-exponential, non-Arrhenius character
% of the relaxations and its correlation with the Poisson ratio of the
% substance.
We present a new, fully {\em ab initio} approach for computing intramolecular charge and
energy transfer rates.  Using a time-convolutionless master-equation approach, parameterized
with couplings obtained from an accurate quantum-chemical approach, we  benchmark the approach
against  experimental results and predictions from Marcus theory for triplet energy transfer for a
series of donor-bridge-acceptor systems.
An important component of our analysis is the use of a projection operator scheme
that parses out specific internal nuclear motions that accompany
the electronic transition.
Using an iterative Lanczos method, we  concentrate the coupling between the electronic and nuclear
degrees of freedom into a small number of reduced harmonic modes.
We find that  using only a single reduced mode--termed the ``primary mode'' or ``Lanczos modes'',
 one obtains an accurate evaluation of the golden-rule rate constant and
insight into the nuclear motions responsible for coupling the initial and final electronic states.
